---
title: "Relationship Between Working Adults, Their Mental Fatigue Score, and Burn Rate"
description: |
  The transition to the online environment hasn't only affected students, but also adults as well. Data on a sample of 100 adult employees was taken and analyzed. From the variables taken from the experiment, I chose to compare if they could work from home, each of their mental fatigue score, and their burn rate from working. From the graph below, we can conclude that adults that don't have access working from home tend to have more of a burn rate with roughly the same mental fatigue score.
date: "`r Sys.Date()`"
output: distill::distill_article
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(tidyverse)
library(lubridate)
library(ggplot2)
library(janitor)
library(ggthemes)
library(data.table)
library(distill)


adult_raw_data <- read_csv("train.csv")
```

```{r, echo= FALSE, fig.height= 3, fig.width = 8}


adult_clean_data <- adult_raw_data %>%
  filter(`WFH Setup Available` %in% c("Yes", "No")) %>%
  select(`WFH Setup Available`, `Mental Fatigue Score`, `Burn Rate`) %>%
  group_by(`WFH Setup Available`) %>%
  drop_na() %>%
  head(100)


adult_clean_data %>%
  ggplot(mapping = aes(x= `Mental Fatigue Score`, y =`Burn Rate`)) +
  geom_jitter() +
  facet_wrap(~`WFH Setup Available`) +
  geom_smooth(method = "lm", formula = y~x) +
  labs( title = "How are adult employees burning out?",
        subtitle = "More adults who don't have access to working from home are buring out faster than adults who do",
        x = "Mental Fatigue Score",
        y = "Burn Rate")

```

### Interpretation

Before looking at the graph to show the results, I would expect employees at home to burn out more than employees at an office setting because with sitting at home for long periods of time and feeling "trapped" inside their houses. Surprisingly, the results showed that employees that didn't have access and have to work at an office actually have a higher mental fatigue score and a faster burn rate. With both categories very high, it shows that home working workers feel tired faster and more doing their job than others who work in person.


^[https://www.kaggle.com/blurredmachine/are-your-employees-burning-out?select=train.csv]



