---
title: "Relationship Between Online Class Experience and Self Studying"
description: |
 With schools transitioning into online learning as a result of the pandemic, many students have struggled transitioning into a new learning environment. As a result, lots of students haven't been able to learn the content of a course through the traditional teaching time, which led many to adapt to self-studying and relying on themselves to learn the content. This graph here analyzes the relationship between those who had different Online class experiences and their time spent on self learning the material.
output: distill::distill_article
---

```{r setup, include=FALSE }
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(lubridate)
library(ggplot2)
library(janitor)
library(ggthemes)
library(data.table)
library(distill)
library(ggdist)

raw_data <- read_csv(file = "COVID-19 Survey Student Responses.csv.xls")



```

```{r, echo = FALSE, fig.height= 3, fig.width = 9}

vec <- c("Very poor", "Average", "Good", "Excellent")
vec_updated <- factor(vec)

clean_data <- raw_data %>%
  filter(`Rating of Online Class experience` %in% c("Excellent", "Average", "Good", "Very poor"))%>%
  mutate(`Rating of Online Class experience` = factor(`Rating of Online Class experience`, levels = vec)) %>%
  select(`Rating of Online Class experience`, `Time spent on self study`) %>%
  group_by(`Rating of Online Class experience`)


  

clean_data %>%
  ggplot(mapping = aes( x = `Time spent on self study`, fill = `Rating of Online Class experience`))+
  stat_slab(position = "dodge") +
  labs(title = "Relationship between Online Class Experience and Self Study Time",
       subtitle = "Students that don't adapt to Online learning as well as others tend to spend more time self-teaching material usually covered in a classroom",
       x = "Time Spent On Self Study (Hours)",
       y = "") +
  theme_minimal() 
  









```

### Interpretation 

Before graphing the data, the topic of experience in class versus the time spent studying was one that was super interesting because it was a topic that I've personally experienced and I'm sure many others. As a hypothesis, I predicted that the lesser experience they get from their online classes would result in a greater amount of time studied; however, when graphing this set of data, the results said else wise. While there were some subjects that did have results like I predicted, the majority or most of the students spent the same amount of time studying regardless of their online class experience. They all approximately spent 2.5 hours on self study. 


^[https://www.kaggle.com/kunal28chaturvedi/covid19-and-its-impact-on-students]

