---
title: "COVID-19 Effect on relationship between Age and Health Issues During Lockdown"
description: |
  This one also looks at adults along with students. One of the consequences or side effects of schools/jobs having their work transfer to an online platform is having students or employees locked at home for at least eight hours watching a screen. Especially with the suspension of sports, closing of gyms, this left people without a reliable mean of exercise and having them stay inside all day on their devices. Reasonably, this lead to a spike in health issues among youthWhile this one also includes physical health when looking at Heath Issues, it is still a really important factor to look at along with mental health. After all, physical health issues can also lead to mental health issues. 
date: "`r Sys.Date()`"
output: distill::distill_article
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(tidyverse)
library(lubridate)
library(ggplot2)
library(janitor)
library(ggthemes)
library(data.table)
library(distill)
library(ggdist)


raw_data <- read_csv(file = "COVID-19 Survey Student Responses.csv.xls")

```


```{r, echo= FALSE, fig.height= 3, fig.width = 8}

age_health_data_group <- raw_data %>%
  select(`Age of Subject`, `Health issue during lockdown`) %>%
  group_by(`Age of Subject`) %>%
  mutate(total_age = n())


age_health_data_group["age_group"] = cut(age_health_data_group$`Age of Subject`, c(0, 10, 20, 30, 40, 50, 60), c("0-10", "11-20", "21-30", "31-40", "41-50", "51-60"), include.lowest=TRUE)

age_health_data_group %>%
  ggplot(mapping = aes(x= age_group, fill = `Health issue during lockdown` ))+
  geom_bar(aes( y = after_stat(count)), color="black")+
  theme_classic() +
  labs(title= "Relationship between Age and Health Issues During Lockdown",
       subtitle = "A significant portion of new health issues during lockdown have occured more in younger ages than older ages ",
       x= "Age Group")

age_health_data_group <- as.data.frame(age_health_data_group)
```

### Interpretation

Before analyzing the data set and graphing the data, I hypothesized that the older the health group, the more health issues would occur because with aging, people's immune system weakens leading to more invulnerability to diseases and illnesses; however, with this data set, it wasn't really clear if this was the case or not. This data gave more of the ratio of health issues in it's own group compared to the number of general health issues during the lockdown. Additionally, this graph shows that there were way more 11-20 and 21-30 year olds surveyed than other other age group which can be misleading. For a more definitive answer, there has to be more data and an equal count of age group surveyed.

^[https://www.kaggle.com/kunal28chaturvedi/covid19-and-its-impact-on-students]



